Estimation of Intracortical Connectivity in a Dynamical Neural Field Model

### 2010-06-22 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added PLoS template and bst and started converting our paper, yay!
trying to add algorithm as a table

   	\caption{An example of a continuous one-dimensional continuous field decomposed by a finite number of basis functions scaled by the state vector.} 

@@

\begin{table}[h!]\footnotesize
    \begin{tabular}{ll}
        $\hat{\mathbf{x}}$ & State estimate \\
	$\chi$ & Matrix of sigma vectors \\
	$\lambda$& Scaling parameter\\
	$\alpha$& Determines the spread of sigma points\\
	$\beta$& Priro knowledge of the sigma points distribution\\
	$\kappa$& Scaling parameter\\
	$W$& Sigma vecors weights\\
    	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate \\
    	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate \\
    	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate \\
    	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate \\
    	$P^f_t$ & Forward posterior covariance matrix \\
    	$P^{f-}_t$ & Forward prior covariance matrix \\
    	$P^b_t$ & Backward posterior covariance matrix \\
    	$P^{b-}_t$ & Backward prior covariance matrix \\
	$\mathcal K_{t} $& Filter gain\\
	$M_t$& Cross-covariance matrix\\
	$S_t$& Smoother gain
    \end{tabular}
    \caption{State Estimation}
\end{table}

>>>>

   	\caption{An example of a continuous one-dimensional field decomposed by a finite number of basis functions scaled by the state vector.} 

@@

\begin{table}[h!]\footnotesize
    \begin{tabular}{ll}
        $\hat{\mathbf{x}}$ & State estimate \\
	$\chi$ & Matrix of sigma vectors \\
	$\lambda$& Scaling parameter\\
	$\alpha$& Determines the spread of sigma points\\
	$\beta$& Prior knowledge of the sigma points distribution\\
	$\kappa$& Scaling parameter\\
	$W$& Sigma vecors weights\\
    	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate \\
    	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate \\
    	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate \\
    	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate \\
    	$P^f_t$ & Forward posterior covariance matrix \\
    	$P^{f-}_t$ & Forward prior covariance matrix \\
    	$P^b_t$ & Backward posterior covariance matrix \\
    	$P^{b-}_t$ & Backward prior covariance matrix \\
	$\mathcal K_{t} $& Filter gain\\
	$M_t$& Cross-covariance matrix\\
	$S_t$& Smoother gain
    \end{tabular}
    \caption{State Estimation}
\end{table}

### 2010-06-22 ltx/PLoS/LaTeX_Manuscript.tex
trying to add algorithm as a table

Mathematical neural field models provide insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see \cite{Deco2008,David2003} for recent reviews). These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) \cite{Liley1999,RENNIE2000}, epileptic seizure generation \cite{DaSilva2003,Suffczynski2004,Wendling2005} and insights into other pathologies \cite{Moran2008,Schiff2009} that would be difficult to gain from experimental data alone.

@@

where $\boldsymbol{\psi}(r,r')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters. By assuming a Gaussian isotropic connectivity structure, the kernel basis functions can be written as $\psi(\mathbf{r}-\mathbf{r}')$. We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown. Each connectivity basis function can, individually, be considered a layer in the Wilson and Cowan model. Typically, the Mexican hat connectivity kernel is comprised of two basis functions representing local excitation and surround inhibition. To demonstrate the flexibility of the estimation framework, a third basis function is incorporated, corresponding to weaker mid-range excitation. Making substitutions of equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} into~\ref{DiscreteTimeModel} we get 

@@

% Results and Discussion can be combined.
\section*{Results}

@@

>>>>

Mathematical neural field models provide insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see~\cite{Deco2008,David2003} for recent reviews). These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) \cite{Liley1999,RENNIE2000}, epileptic seizure generation \cite{DaSilva2003,Suffczynski2004,Wendling2005} and insights into other pathologies \cite{Moran2008,Schiff2009} that would be difficult to gain from experimental data alone.

@@

where $\boldsymbol{\psi}(\mathbf{r},\mathbf{r}')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters. By assuming a Gaussian isotropic connectivity structure, the kernel basis functions can be written as $\psi(\mathbf{r}-\mathbf{r}')$. We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown. Each connectivity basis function can, individually, be considered a layer in the Wilson and Cowan model. Typically, the Mexican hat connectivity kernel is comprised of two basis functions representing local excitation and surround inhibition. To demonstrate the flexibility of the estimation framework, a third basis function is incorporated, corresponding to weaker mid-range excitation. Making substitutions of equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} into~\ref{DiscreteTimeModel} we get 

@@

% Results and Discussion can be combined.
\section*{Results}\label{ResultsSection} In this section we provide a demonstration of the estimation procedure using the methods described above. The full neural field model derived in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation. All parameters for the model are given in Table~\ref{tab:Model Parameters}. Note that, the parameters for the spatial and temporal aspects of the model can be considered arbitrary when demonstrating the estimation methodology. This is due to the fact that the temporal aspects scale with the sampling rate and the length of the times series, and the spatial aspects scale with the size of the neural field and the space step used for numerical simulation. When generating the simulated data we assumed free boundary conditions for the neural field. An example of the simulated field can be seen in Figure~\ref{fig:experimental design}(a). Figure~\ref{fig:experimental design}(b) shows an example of data from the modelled sensors and Figure~\ref{fig:experimental design}(c) shows the power spectral density (PSD) of the simulated time-series. The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
\begin{table}\footnotesize
\centering
\begin{tabular}{ccl}
	\hline\hline Symbol & Value & Units \\
	\hline\hline
	$\tau$ & 0.01 & s$^{-1}$\\
	$f_{max}$ & 10 & spikes/s \\
	$\varsigma$ & 0.8 & spike/mV\\
	$v_0$ & 2 & mV\\
	$\boldsymbol{\theta}$ & $\left[\begin{array}{ccc}
	10 &-8 &0.5
	\end{array}
	\right]^{\top}$ & mV/spike\\
	$\sigma_{\psi_{1}}, \sigma_{\psi_{2}}, \sigma_{\psi_{3}}$ & 1.8, 2.4, 6 & mm\\
	$\sigma_{m},\Delta_{y}$&0.9, 1.5&mm\\
	$\Sigma_{\epsilon}$ &$0.1 \times I_{N} $& mm$^2$ \\
	$\sigma_{\gamma}$&1.3&mm\\
	$\Delta$ & 0.5 & mm \\
	$T_s$ & 1 & ms \\ 
\hline\hline
\end{tabular}
\caption{Parameters for the neural field model that are used to generate synthetic data.}
\label{tab:Model Parameters}
\end{table}

The sensors were spaced on a regular square $14 \times 14$ grid, the sensor width was set to $\sigma^2_m = 0.81$. This provides a width of $1.5$~mm at half the maximum amplitude of the basis function, with spacing $\Delta_y = 1.5$~mm. This arrangement modelled the recording as having some cross talk, which is typical for neurophysiological recordings. 
% \begin{figure}
%    	\begin{center}
%     		\subfigure[][]{\includegraphics{./Graph/ExperimentFigurePy.pdf}} \\
%     		\subfigure[][]{\includegraphics{./Graph/ExperimentFigureEEGPy.pdf}} \\
%    		\subfigure[][]{\includegraphics{./Graph/ExperimentFigurePSDPy.pdf}} \\
%    	\end{center}
%    	\caption{\textbf{a.} Example of the neural feld. \textbf{b.} Example of data generated by the full neural field model from the first 5 sensors. \textbf{c.} Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of intracranial EEG.} 
% \label{fig:experimental design}
% \end{figure}
\subsection*{Spatial Frequency Analysis} 
Using the model selection techniques described in Section~\ref{SpectralAnalysisSection}, the spatial frequency analysis was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field. Figure~\ref{fig:FieldFFT} shows the spatial frequency of the neural field. The cut-off frequency of the neural field is $\nu_c \approx 0.24$~Hz ($-3$~dB point). From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of $2.05$~mm. This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to prevent problems associated with spatial aliasing.
% \begin{figure}
% \centering
% \subfigure[][]{\label{fig:FieldFFT}\includegraphics{./Graph/FFTTrueField.pdf}}
% \subfigure[][]{\label{fig:EstimatedFieldFFT}\includegraphics{./Graph/FFTEstimatedField.pdf}}\\
% \caption{Spatial frequency analysis of the neural field. \textbf{a.} The average (over time) power in dB of the spatial frequency of the neural field. \textbf{b.} The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition. The reconstructed field shows a narrower bandwidth as a result of the band limiting properties of the sensors and basis functions.}
% \label{fig:FFTTrueEstimate}
% \end{figure}
The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}. The cut-off frequency is $\nu_{cy} \approx 0.2$~Hz ($-3$~dB point). The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors. The spatial frequency response of the sensors can be seen in Figure~\ref{fig:SensorFunctionFreqResponse}. Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be $2.5$~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}). The distance between basis functions was set to $\Delta_{\phi}=2.5$~mm, which is sufficient to capture the significant dynamics according to our criteria.
Given the basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$~mm. This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\mathbf{\nu_{c\phi}} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}. The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:BasisFunctionFreqResponse}.
% \begin{figure} 
% 	\begin{center}
% 		\subfigure[][]{\label{fig:ObservationFreqAnal}\includegraphics{./Graph/ObservationFrequencyResponse.pdf}}\\	
% 		\subfigure[][]{\label{fig:SensorFunctionFreqResponse}\includegraphics{./Graph/SensorChar.pdf}}
% 		\subfigure[][]{\label{fig:BasisFunctionFreqResponse}\includegraphics{./Graph/BasisChar.pdf}}
% 	\end{center}
% 	\caption{Spatial frequency analysis. The dashed line shows the cut-off frequency (-3 dB point). \textbf{a.} Two-dimensional spatial frequency in power dB, averaged over 400 time steps) of the observed field. The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics. \textbf{b.} The spatial frequency response of a one-dimensional model sensor. \textbf{c.} The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.} 
% \end{figure}

\subsection*{State and Parameter Estimates} 
\label{sec:state_and_param_results}
To demonstrate the performance of the state and parameter estimation algorithm, a Monte Carlo approach was employed where $100$ realisations of the data were generated. Each realisation consisted of $500$~ms of data (sampled at $1$~kHz) and the estimation was applied to the final $400$~ms, allowing the model's initial transients to die out. The initial state and parameters were unknown to the estimator. Eleven iterations of the estimation algorithm were used to ensure the parameters  converged. Figure~\ref{fig:ParametersConvergence} shows the rate of convergence, confirming the parameters converged, with the changes in parameters falling to less than $10^{-4}$ after six iterations.
\begin{figure}
        \centering
\includegraphics{./Graph/convergence.pdf}
\caption{The mean of the absolute error between true and estimated parameters averaged over 100 runs. All parameters converge after six iterations, where the mean difference between errors in consecutive iterations falls below $10^{-4}$.}
\label{fig:ParametersConvergence}
\end{figure}

Histograms of the parameter estimates obtained over the 100 realisations are shown in Figure~\ref{fig:Parameters}. The actual parameter values, the mean estimates, corresponding standard deviations and biases are given in Table~\ref{tab:Parameters estimates}. The biases show the percentage differences between the actual values and the mean parameter estimates. The mean estimates are in good concordance with the actual values. 
% It should be noted that when the excitatory connectivity parameters, $\hat\theta_0$ and $\hat\theta_2$, were under (or over) estimated, the inhibitory connectivity parameter, $\hat\theta_1$, tended to be over (or under) estimated. This is demonstrated in Figure~\ref{fig:ParametersRatio} where we show the distribution of the ratios of the parameter estimates. 
\begin{table}
\centering
\begin{tabular}{cccc}
	\hline\hline Parameter & Actual Value & Mean Estimate $\pm$ Std. Dev. & Bias (\%) \\
	\hline\hline
 	$\xi$ & $0.9$ & $0.925\pm 0.004$ & $2.778$ \\
	$\theta_0$ & $10$ & $10.228\pm2.794$ & $2.28$\\
	$\theta_1$ & $-8$ & $-8.495\pm1.913$ & $-6.187$\\
	$\theta_2$ & $0.5$ & $0.545\pm0.077$ & $9$\\
	% $\mid\theta_0/\theta_1\mid$ &$1.25 $ & $1.189\pm 0.0812$ &$4.88$\\
	% $\theta_0/\theta_2$ &$20$ & $18.567\pm3.757$ &$7.165$ \\
\hline\hline
\end{tabular}
\caption{Actual parameter values compared to parameter estimates.}
\label{tab:Parameters estimates}
\end{table}
% \begin{figure}
%     \centering
%     \subfigure[][]{\includegraphics{./Graph/zeta.pdf}}
%     \subfigure[][]{\includegraphics{./Graph/theta0.pdf}}\\
%     \subfigure[][]{\label{fig:theta1dis}\includegraphics{./Graph/theta1.pdf}}
%     \subfigure[][]{\includegraphics{./Graph/theta2.pdf}}
% \caption{Distribution of the parameter estimates over 100
% realisations. The solid line shows the actual value of the parameters and the dotted line shows the mean of the estimated parameters. \textbf{a.} The distribution of the $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant. \textbf{b.} The distribution of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$. \textbf{c.} The distribution of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$. \textbf{d.} The distribution of the longer range excitatory connectivity kernel basis function parameter estimates, $\theta_2$.}
% \label{fig:Parameters}
% \end{figure}
% \begin{figure}
%     \centering
% \subfigure[][]{\includegraphics{./Graph/theta0_theta1_ratio.pdf}}
% \subfigure[][]{\includegraphics{./Graph/theta0_theta2_ratio.pdf}}\\
% \caption{Distribution of the connectivity kernel basis function parameter ratios over 100 realisations. \textbf{a.} The absolute value of the ratio of the local excitatory parameter to the surround inhibition parameter (true ratio is 1.25). \textbf{b.} The ratio of the local excitatory parameter to the longer range excitatory parameter (true ratio is 20). In each case, the solid and dotted lines show the locations of the true and estimated ratios respectively.}
% \label{fig:ParametersRatio}
% \end{figure}
The reconstructed connectivity kernels from the estimated parameters are illustrated in Figure~\ref{fig:KernelEstimates}, where the mean over the 100 realisations is shown as a dotted line and the $95\%$ confidence interval is indicated by the grey shaded region. The figure verifies that the shape of the estimated connectivity kernel is in good accordance to the true kernel. The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias on the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:theta1dis}.

\begin{figure}
    \centering
% \subfigure[][]{
\includegraphics{./Graph/KernelEstimate.pdf}%}
% \subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT.pdf}}\\
\caption{Cross-section of connectivity kernel estimate. The actual kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dotted line and the $95~\%$ confidence interval is shown by the shaded grey region.}
\label{fig:KernelEstimates}
\end{figure}
The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) (over space). The MRMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}, with the $95~\%$ confidence interval. At each time point the error is consistently around 0.5~mV, which approximately $7.1$~\% of the field voltage range, which is $(-3.29,3.77)$~mV. The error in the reconstructed field is mostly due to the loss of high spatial frequency information due to the basis function decomposition as illustrated in Figure~\ref{fig:FieldEstimate}. The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields. It can be seen in Figure~\ref{fig:FieldEstimate}(b) that the estimated field contains the basic structure of the true field (Figure~\ref{fig:FieldEstimate}(a)), but is missing the higher-frequency detail.
  \begin{figure}
   	\begin{center}
   		\includegraphics{./Graph/MRMSE.pdf} 
   	\end{center}
   	\caption{The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region).} 
\label{fig:RMSE}
   \end{figure}

% \begin{figure}
% \centering 
% \subfigure[][]{\label{fig:TrueField}\includegraphics{./Graph/TrueField90.pdf}}
% \subfigure[][]{\includegraphics{./Graph/EstimatedField90.pdf}}
% \subfigure[][]{\includegraphics{./Graph/EstimationError90.pdf}}\\
% \caption{Examples of the actual and estimated neural fields and the error. \textbf{a.} The actual field at a single time instant from the full neural field model that was used to generate data. \textbf{b.} The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field. \textbf{c.} The absolute error between the true and reconstructed fields. The error shows high frequency behaviour.}
% \label{fig:FieldEstimate}
% \end{figure}

@@

\begin{table}[!ht]
\caption{
\bf{The Unscented RTS Smoother}}
\begin{tabular}{|c|}
\multicolumn{1}{|p{16cm}|}{ 1. Forward initialisation} \\
$\hat{\mathbf x}_0, \mathbf P_0$ \\
\multicolumn{1}{|p{16cm}|}{   Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $, calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}} \\
$\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L$ \\
\multicolumn{1}{|p{16cm}|}{   Calculate the predicted state and the predicted covariance matrix} \\
$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
\end{tabular}
\begin{flushleft}Table caption
\end{flushleft}
\label{tab:label}
\end{table}

\begin{algorithm}
	\begin{small}
	\caption{The Unscented RTS Smoother}\label{UKFAlgorithm} 
	\begin{algorithmic}[1] 
		\State Forward initialisation 
		\begin{equation*}
		 \hat{\mathbf x}_0, \mathbf P_0 
		\end{equation*}
		\State Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $,
		calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}
% 		\begin{small}
		\begin{equation*}
			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L
		\end{equation*}
% 		\end{small}
		calculate the predicted state and the predicted covariance matrix
		\begin{equation*}
			\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} 
		\end{equation*}
		\begin{equation*}
			\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e 
		\end{equation*}
		compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman Filter update equations
		\begin{equation*}
			\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\epsilon})^{-1} 
		\end{equation*}
		\begin{equation*}
			\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) 
		\end{equation*}
		\begin{equation*}
			\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-} 
		\end{equation*}
		\State Backward initialisation 
		\begin{equation*}
			\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T 
		\end{equation*}
		\State Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}
		\begin{equation*}
			\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L
		\end{equation*}
		 compute the predicted state, the predicted covariance matrix and the cross-covariance matrix
		\begin{equation*}
			\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-} 
		\end{equation*}
		\begin{equation*}
			\mathbf P_{t +1}^{b-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})^\top+\boldsymbol \Sigma_e 
		\end{equation*}
		\begin{equation*}
			\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top 
		\end{equation*}
		 Compute the smoother gain, the smoothed state and the smoothed covariance matrix
		\begin{equation*}
			\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} 
		\end{equation*}
		\begin{equation*}
			\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right] 
		\end{equation*}
		\begin{equation*}
			\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top 
		\end{equation*}
	\end{algorithmic}
\end{small}
\end{algorithm}
